Analysis

### 2022-06-03 FIMO_processing.Rmd
Savind extended summary and tweaks

# Input files
fileNameIn1 <- file.path(dir_data, "")
# Output files
fileNameOut1 <- file.path(dir_data, "log_PWMs.csv")
```

@@

  ctcfGR_to_save <- paste(genome_id, motif, "FIMO", sep = ".")
  fileNameOut1 <- file.path(dir_data, paste0(ctcfGR_to_save, ".RData"))
  fileNameOut1.1 <- file.path(dir_data, paste0(ctcfGR_to_save, ".bed"))
  # Assign this object to the subfolder-specific variable name
  assign(ctcfGR_to_save, ctcfGR)
  # Save as RData object. ctcfGR_to_save is the character name of the CTCF GRanges variable
  save(list = ctcfGR_to_save, file = fileNameOut1)
  # load(file = fileNameOut1)
  # export.bed(eval(parse(text = ctcfGR_to_save)), fileNameOut1.1)
  ctcfDF_to_save <- as.data.frame(eval(parse(text = ctcfGR_to_save)))
  ctcfDF_to_save <- ctcfDF_to_save[, c("seqnames", "start", "end", "name", "score", "strand", "width", "pvalue", "qvalue", "sequence")]
  write_tsv(ctcfDF_to_save, fileNameOut1.1, col_names = FALSE)
}
```

@@

```{r}
# for file in `find . -type f -name "*MA0139*"`; do
#   echo $file
#   newfile=`echo $file | sed 's/MA0139/JASPAR2022_MA0139/'`
#   echo $newfile
#   mv $file $newfile
# done
# 
files <- list.files(dir_data, pattern = "*.bed", full.names = TRUE)
for (file in files) {
  print(basename(file) %>% str_remove(., ".bed"))
  mtx <- read_tsv(file, col_names = FALSE)
  colnames(mtx) <- c("seqnames", "start", "end", "name", "score", "strand", "width", "pvalue", "qvalue", "sequence")
  gr <- makeGRangesFromDataFrame(mtx)
  # Summary
  summary_to_save <- data.frame(File = basename(file) %>% str_remove(., ".bed"),
                                Assembly = strsplit(basename(file), ".", fixed = TRUE)[[1]][1],
                                All = length(gr),
                                Reduced = length(reduce(gr)))
  write_csv(summary_to_save, fileNameOut1, append = TRUE)
}
```

>>>>

# Input files
fileNameIn1 <- file.path(dir_data, "")
```

@@

  ctcfGR_to_save <- paste(genome_id, motif, sep = ".")
  fileNameOut1 <- file.path(dir_data, paste0(ctcfGR_to_save, ".RData"))
  fileNameOut1.1 <- file.path(dir_data, paste0(ctcfGR_to_save, ".bed"))
  # Assign this object to the subfolder-specific variable name
  assign(ctcfGR_to_save, ctcfGR)
  # Save as RData object. ctcfGR_to_save is the character name of the CTCF GRanges variable
  save(list = ctcfGR_to_save, file = fileNameOut1)
  # load(file = fileNameOut1)
  # export.bed(eval(parse(text = ctcfGR_to_save)), fileNameOut1.1)
  ctcfDF_to_save <- as.data.frame(eval(parse(text = ctcfGR_to_save)))
  ctcfDF_to_save <- ctcfDF_to_save[, c("seqnames", "start", "end", "name", "score", "strand", "width", "pvalue", "qvalue", "sequence")]
  write_tsv(ctcfDF_to_save, fileNameOut1.1, col_names = FALSE)
}
```

@@

```{r}
# for file in `find . -type f -name "*MA0139*"`; do
#   echo $file
#   newfile=`echo $file | sed 's/MA0139/JASPAR2022_MA0139/'`
#   echo $newfile
#   mv $file $newfile
# done
# 
# Output files
fileNameOut1 <- file.path(dir_data, "log_PWMs.csv")
if (file.exists(fileNameOut1)) { file.remove(fileNameOut1) }
# Defined from FIMO_EDA
pval_threshold <- 1e-6
files <- list.files(dir_data, pattern = "*.bed", full.names = TRUE)
for (fil in files) {
  print(basename(fil) %>% str_remove(., ".bed"))
  mtx <- read_tsv(fil, col_names = FALSE, col_types = c("ciicdciddc"))
  colnames(mtx) <- c("seqnames", "start", "end", "name", "score", "strand", "width", "pvalue", "qvalue", "sequence")
  gr <- makeGRangesFromDataFrame(mtx, keep.extra.columns = TRUE)
  # Summary
  summary_to_save <- data.frame(File = basename(fil) %>% str_remove(., ".bed"),
                                Assembly = strsplit(basename(fil), ".", fixed = TRUE)[[1]][1],
                                `All (p-value threshold 1e-4)` = length(gr),
                                `Reduced (p-value threshold 1e-4)` = length(reduce(gr)),
                                `All (p-value threshold 1e-6)` = length(gr[gr$pvalue < pval_threshold]),
                                `Reduced (p-value threshold 1e-6)` = length(reduce(gr[gr$pvalue < pval_threshold])) )
  write_csv(summary_to_save, fileNameOut1, append = TRUE)
  gc()
}
```
